Inference of Bifurcations\\with Differentiable Continuation

### 2021-05-17 docs/article.tex

\begin{figure}
    \centering
    \includegraphics[width=10cm]{bifurcation-measure}
    \caption{Bifurcation measure $\measure(z)$ shown as a gold thickness envelope. The thicker the envelope the larger the value of the measure at that location in the curve. Three curves are shown for three different values $\theta$, demonstrating how maximising $\measure(z)$ along the curve encourages new bifurcations}
    \label{fig:bifurcation-measure}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=7cm]{bifurcation-measure}
    \caption{Bifurcation measure $\measure(z)$ and determinant $\Det$ for two different bifurcation curves demonstrating how maximising the measure along the curve maintains the existing bifurcation marked by a circle, while encouraging new bifurcations marked by stars}
    \label{fig:bifurcation-measure}
\end{figure}
